---
title: "MTH 6312:methodes statistiques dapprentissage-Ex03"
author: "Reza Rad"
date: "September 23, 2015"
output: html_document
---
1.Find an interesting project and a data set as your project. Write two paragraphs about your
suggested projects. Argue why I must pay 50 $ to see the result of your data analysis.



2.**(Where do you buy a house in Chicago?)** The crime data of Chicago are publicly available here
[link](https://data.cityofchicago.org/Public-Safety/Crimes-2001-to-present/ijzp-q8t2)
Take the subset of crimes commited in 2015 and plot a red dot (with enough transparency) for
each theft appeared during 2015 until today on googlemap.
Hint: Use get map, and ggmap functions from ggmap library to download the google map with
appropriate zoom, longitude, and latitude. Then add red points using geom point function of
ggplot2 library with transparency on your Chicago map. See the sample of the next page. PS:
Using ggplot functions is not straightforward, check some simple examples first, before trying
to overlay your points on the map.

```{r,message=FALSE}
library(MASS)
require(ggplot2)
require(ggmap)
D=read.csv("Crimes.csv",header = TRUE)
lon=D$Longitude
lat=D$Latitude
mymap= get_map(location="chicago",zoom=11,scale="auto",maptype="roadmap")
ggmap(mymap)+
  geom_point(data=as.data.frame(cbind(lon,lat)),aes(x=D$Longitude,y=D$Latitude),color="red",alpha=.01,size=1,shape=21)

```


3. Plot the univariate density of thefts of 2015 over latitude plot(density()) the sample of
the next page.



```{r,message=FALSE}
require(ggplot2)
require(ggmap)
#D=read.csv("Crimes.csv",header = TRUE)
lon=D$Longitude
lat=D$Latitude
plot(density(na.omit(D)$Latitude),xlab="latitude",col="blue",main="Density over latitude")
```


4.Compute he 2D density using kde2d function of library MASS and use persp function to
provide a 3D plot. See the sample of the next page.


```{r,message=FALSE}
library(MASS)
require(ggplot2)
require(ggmap)
#D=read.csv("C:/Users/BABAK/Desktop/Crimes.csv",header = TRUE)
lon=D$Longitude
lat=D$Latitude
persp(kde2d(na.omit(D)$Latitude,na.omit(D)$Longitude),phi = 45, theta = 0,
      xlab = "Lat", ylab = "Long",zlab = "density")

```






